COMPAS Race Analysis

### 2022-03-28 race compas analysis.Rmd
adding table of race and recidivism

```{python}
# recividism by race
by_sex = sns.countplot(x="race", hue="two_year_recid", data=df_viz, palette=workshop_palette)

@@

>>>>

```{python}
# recidivism by race
by_sex = sns.countplot(x="race", hue="two_year_recid", data=df_viz, palette=workshop_palette)

@@

```{python}
# table of recidivism by race
pd.crosstab(index = df_viz["race"], columns = df_viz["two_year_recid"])
```
